Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2015-05-26 cordillera-cycle.tex
Enhance profile labelling using capital letters.

\begin{figure}
  \includegraphics{profiles-grip}
  \caption{Modelled bedrock (black) and ice surface (blue) topography profiles
           during deglaciation (22.0--8.0\,ka) in the GRIP 5\,km
           simulation, corresponding to the four transects indicated in
           Figs.~\ref{fig:deglacshots}--\ref{fig:lastflow}.}
  \label{fig:profiles-grip}
\end{figure}

\begin{figure}
  \includegraphics{profiles-epica}
  \caption{Modelled bedrock (black) and ice surface (red) topography profiles
           during deglaciation (22.0--8.0\,ka) in the EPICA 5\,km
           simulation, corresponding to the four transects indicated in
           Figs.~\ref{fig:deglacshots}--\ref{fig:lastflow}.}
  \label{fig:profiles-epica}
\end{figure}

>>>>

\begin{figure}
  \includegraphics{profiles-grip}
  \caption{Modelled bedrock (black) and ice surface (blue) topography profiles
           during deglaciation (22.0--8.0\,ka) in the GRIP 5\,km
           simulation, corresponding to the four transects indicated in
           Figs.~\ref{fig:deglacshots} and~\ref{fig:deglac}.}
  \label{fig:profiles-grip}
\end{figure}

\begin{figure}
  \includegraphics{profiles-epica}
  \caption{Modelled bedrock (black) and ice surface (red) topography profiles
           during deglaciation (22.0--8.0\,ka) in the EPICA 5\,km
           simulation, corresponding to the four transects indicated in
           Figs.~\ref{fig:deglacshots} and~\ref{fig:deglac}.}
  \label{fig:profiles-epica}
\end{figure}
